Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-11-26 ICLR25/proofsb.tex
update

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|}
		\hline
		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
		5  & 1.729& 1.7138 &  &\bf 1.532 \\ \hline
		10  & 1.696 & 1.6775& &\bf  1.371\\ \hline
		15  &   1.653& 1.6392& &\bf  1.247\\ \hline
		20  &   1.619 &1.5938 & &\bf  1.145\\ \hline
		25  &    1.586 &1.5534 & &\bf 1.061\\ \hline
		30  &  1.546 & 1.5166& &\bf  0.989 \\ \hline
		35  &   1.502 & 1.4788 & &\bf 0.934 \\ \hline
		40  &  1.469 & 1.4395& &\bf 0.921 \\ \hline \hline
		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
	\end{tabular}
	\caption{BSR and FSB}
	\label{BSRandFSB}
	%\vspace{-0.6cm}
\end{table}

>>>>

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|}
		\hline
		&\multicolumn{3}{c|}{$X \subseteq$ Layers 1\&2, max $=116$}\\\cline{2-5}
		\text{$|X|$} & \text{Random} &BSR &FSB &\bf Utility\\ \hline
		0  (LP) & 1.761  &  1.761& 1.761&1.761\\ \hline \hline
		5  & 1.729& 1.7138 & 1.7182 &\bf 1.532 \\ \hline
		10  & 1.696 & 1.6775&  1.6803&\bf  1.371\\ \hline
		15  &   1.653& 1.6392& 1.6475&\bf  1.247\\ \hline
		20  &   1.619 &1.5938 & 1.6174&\bf  1.145\\ \hline
		25  &    1.586 &1.5534 &1.5788 &\bf 1.061\\ \hline
		30  &  1.546 & 1.5166& 1.5413&\bf  0.989 \\ \hline
		35  &   1.502 & 1.4788 &1.4972 &\bf 0.934 \\ \hline
		40  &  1.469 & 1.4395& 1.4514&\bf 0.921 \\ \hline \hline
		max &  0.895 & 0.895 &0.895 &0.895   \\ \hline
	\end{tabular}
	\caption{BSR and FSB}
	\label{BSRandFSB}
	%\vspace{-0.6cm}
\end{table}
